\subsection{DNA Cloning}
DNA cloning was concluded by sequencing of the plasmids and the calculation of the yield from the midi preparation. The full agreement of the sequencing result with the designed sequences enables further use of the plasmids in cell-free expression. The yields of the midi preparation are slightly lower than the manufacturer's reported typical yield of \SI{500}{\micro\gram}, but still high enough to allow for use in cell-free expression after concentration. 

\subsection{Protein Expression}
\subsubsection{eYFP Yield by Fluorescence}
Following cell-free expression, the protein yield of the batch was estimated by fluorescence measurements of the Strep-eYFP reaction setup. The determined concentration of \SI{0.3}{\milli\gram\per\milli\litre} is significantly lower than the manufacturer's reported typical yield of at least \SI{2}{\milli\gram\per\litre}. Typical reasons for low lysate performance, as stated by the manufacturer, are an inappropriate amount of plasmid DNA, poor oxygenation, or expired lysate. As for the plasmid DNA, the manufacturer explains that the optimal amount varies for each protein and should be determined by testing. Potentially, use of less DNA could improve the yield. Oxygenation in this setup was provided through a hole in the reaction tube's lid. An optimal oxygen supply could be established by using the dedicated perforated lids shipped with newer versions of the lysate. Use of newer lysate might also lead to a higher yield, since deterioration of the kit's components is a known issue 

\subsubsection{Coomassie Staining and Western Blot}
Evaluation of the cell-free expression's qualitative success, as well as of the CaptoCore chromatography, was conducted through Western Blots using an anti-PVX antibody and an anti-S-Tag antibody.

After the Coomassie staining of the ALiCE reaction mixture, the samples d29-A, S-Tag-A, and S-Tag-B, showed no notable difference from the non-template control, while the tracks containing expression mix from the PVX CP and the Strep-eYFP setup display bands at molecular weights matching the control. This could imply a lower yield in these setups. However, the bands from other proteins in the lysate provides bad contrast, and visual differences might simply be caused by the fact that the bands are at slightly different heights than those of Strep-eYFP, and possibly worse to distinguish from the background. Further, the control S-Tag-CP-PVX only displays a faint band as well, reinforcing that there is no sure implication on the yield. 

The anti-PVX Western Blot shows defined bands for d29-A, S-Tag-A, and PVX CP, but only a very faint band for S-Tag-B. This could be due to a lower yield for S-Tag-B, or less avidity of the anti-PVX antibody against the protein, given that it only has \SI{0.53}{\percent} sequence identity to the wild type. For all samples and the control S-Tag-CP-PVX, the migration of distance suggested a molecular weight higher than the theoretical one. For PVX particles from plants, this is a well-known phenomenon and partly due to specific glycosylations of the proteins \cite{pvx_glycosylation}. However, glycosylation of the ALiCE samples is unlikely, since they were expressed through the cytosolic pathway. The discrepancy with the theoretical weights might imply partial aggregation. Binding of the anti-PVX antibody against the d29-A and S-Tag-A and the faint signal for S-Tag-B could indicate that the coat proteins partially folded into the desired shape. However, the anti-PVX antibody is polyclonal, and it is not clear whether its epitopes are specific to the protein's fold. 

In the Western Blot using the anti-S-Tag antibody, both samples S-Tag-A and S-Tag-B show a strong signal, implying that the antibody has high avidity against them. The signal is not constrained to the migration distance as seen in the anti-PVX blot, but is faintly visible through most of the track. Signal at larger molecular weights might stem from aggregates, while signal at lower molecular weights suggests the existence of smaller protein parts containing an S-Tag, possibly through partial degradation of the protein while boiling the samples. 

Following CaptoCore purification, no discernible bands were visible in the Coomassie gel or the Western Blot. The signals in the first iteration of the Western Blot likely arose from column resin permeating the filter and carrying protein with it. However, it is also possible that the signal in the first batch actually stemmed from specific or unspecific protein complexes that did not form in the second batch. This is rendered unlikely since, in the first blot, the wild type PVX CP also showed a signal, even though it is known to not assemble in absence of its genome \cite{juli_sagt_keine_assembly}. In any case, the Western Blot following CaptoCore purification indicates that there were little to no assembled complexes in the reaction mixture. 

\subsubsection{ELISA}
For a quantitative analysis of the cell-free expression of d29-A, S-Tag-A, S-Tag-B, and PVX CP, ELISAs using both anti-PVX and anti-S-Tag antibodies were conducted. 

In both cases, the optical densities of the samples were almost identical for the 1:500 and the 1:1000 dilution. This might be caused by other proteins in the lysate saturating the binding capacity of the microwell plate, even at the stronger dilution, and thus rendering only the proportion of the specific protein in the reaction mixture relevant. Under this assumption, the result from the 1:1000 dilution would be more significant, even though in general stronger dilutions should be tested to get a better estimate. 

Using the 1:1000 dilution, the highest protein concentration in the anti-PVX ELISA was observed for the PVX CP, with a calculated concentration of \SI{134}{\micro\gram\per\milli\litre}. This is less than half the value measured for Strep-eYFP expression by the lysate. A possible cause is lower expression or quicker degradation of the protein in the reaction mixture. A different reason could be that the antibody has higher avidity for the assembled viral particles than for the PVX CP in the ALiCE expression mix, which are known to not assemble without specific RNA present \cite{pvx_assembly}. This is plausible, since the antibody was generated by rabbit immunization against viral particles. For the constructs d29-A, S-Tag-A, and S-Tag-B, the anti-PVX ELISA leads to lower calculated concentrations of about \SI{30}{\micro\gram\per\milli\litre} for d29-A and S-Tag-A, and no discernible signal for S-Tag-B. This could also be due to lower avidity of the antibody towards the adapted sequences. The missing signal for S-Tag-B is consistent with the anti-PVX Western Blot, which showed only a very faint line for S-Tag-B. 

Using the anti-S-Tag antibody, only the samples from S-Tag-A and S-Tag-B had significant optical densities. The back-calculated concentrations of \SI{2.4}{\milli\gram\per\milli\litre} and \SI{1.2}{\milli\gram\per\milli\litre} are very high, and unlikely given the measured expression of only \SI{0.3}{\milli\gram\per\milli\litre} for the Strep-eYFP ALiCE control setup. Possibly, the anti-S-Tag antibody has considerably higher avidity against protein monomers than for the assembled particles in the calibration samples. This could explain the high optical density, since the faint signal in the CaptoCore after the Western Blot implies that little to no protein in the ALiCE setup assembled. Notably, the anti-S-Tag antibody is not explicitly labeled as being suitable for ELISA, so the high signal might also be due to this, even though the calibration showed a linear trend with high determination.

\subsubsection{Electron Microscopy}
The electron microscopy, conducted to analyze whether assembled particles were present in the purified ALiCE reaction mixture, showed no signs of VLP formation for the constructs d29-A, S-Tag-A, as well as the expressed PVX CP. The visible dark clumps in the images also appear in the non-template control and are thus likely not related to the specific expressed protein, but rather to other components of the lysate that passed the CaptoCore column. This observation is in line with the absence of a signal in the Western Blots after the purification. 

The control sample of S-Tag-PVX virions clearly showed the filamentous, flexible structure of PVX virions as described by Grinzato et al. The measured size of \SI{17}{\nano\meter} in diameter and about ~\SI{600}{\nano\meter} in length agree with values from literature of a diameter of \SI{15}{\nano\meter} and a modal length of ~\SI{500}{\nano\meter}. 

One of the two rod-like structures found in the purified reaction mix of S-Tag-B also has the shape of PVX virions, with a measured diameter of \SI{15}{\nano\meter}, a length of \SI{760}{\nano\meter}, and a flexible structure. The other structure is thicker than PVX, with a measured diameter of \SI{24}{\nano\meter}. Both could potentially indicate assembly of S-Tag-B coat proteins into helical complexes. However, the fact that only two of those structures were found in the sample make this result unsure. Clarification on whether or not these structures are actually made up of S-Tag-B monomers could be achieved by using immunoelectron microscopy (exemplary image in \autoref{fig:em_immuno_labeling}).

