\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgments}

Computations were performed with computing resources granted by RWTH Aachen University under project rwth1801.

\vspace{0.5cm}

\noindent \textbf{Thanks to:}

Stefan Schillberg, for the opportunity to write my thesis at the institute and for providing the framework that brought together such an incredible team.

\vspace{0.3cm}

To Anna Matuszynska, for her willingness to appraise my thesis, for being such an inspiring role model of mathematicians in biology, and for single-handedly carrying me through all of my applications in recent years. If I become someone someday, it will be because of you!

\vspace{0.3cm}

Thanks to Juliane, for her support in carrying out my wet lab work, and her unconditional trust in my ability to handle the dry lab coding. I think it takes a special kind of courage and interdisciplinary skill to encourage and supervise projects outside of your usual expertise.

\vspace{0.3cm}

Thanks to the Bio7 team for providing this wonderful environment to work and thrive in. If there's one thing I regret about this thesis, it's that I so often failed to schedule my experiments in a way that would let me have lunch with you all.

\vspace{0.3cm}

Thanks to Sebastian for your emotional support and for teaching me everything about \LaTeX{} that you don't learn as a mathematician.

\vspace{0.3cm}

Thanks to my family for supporting my studies through not one but two bachelor's degrees. I promise, I'm heading somewhere!